---
title       : Prediction
subtitle    : Predicting MPG based on Weight and Transmission type
author      : 
job         : 
framework   : io2012     # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
--- {class: class1, id: id1, bg: lightyellow}

## Goal

* Predict MPG using weight and transmission type

* mtcars dataset is used to train the model

* A simple linear model

* Use the model to predict for new observations

--- {class: class1, id: id1, bg: lightyellow}

## Correlation Plot

```{r, echo=FALSE}
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
```


```{r,fig.width=10, fig.height=4}

data(mtcars)

mpg_plot <- ggplot(mtcars, aes(x = wt, y=mpg)) + geom_point()

wt_plot <- ggplot(mtcars, aes(x = am, y=mpg)) + geom_point()

multiplot(mpg_plot,wt_plot, cols=2)

```

--- {class: class1, id: id1, bg: lightyellow}
## Model
```{r}

fit <- lm(mpg~wt+am, data=mtcars)

fit

```

--- {class: class1, id: id1, bg: lightyellow}
## Conclusion

* The weight turns to be significant factor in determining the MPG

* We have build a web page where we can provide new observations and predict the MPG

* https://cvsekhar.shinyapps.io/dataproduct/


